### 2017-02-01 thesis/results/results2.tex
Added figure images into results; tmp commit

\chapter{Results from gatza pathway metagene and direction stuff}

\section{Reproducing results from gatza paper}

>>>>

\chapter{Obesity associated genetic signatures and pathway signatures}
\label{cha:obesity_associated_genetic_signature_and_pathway_signatures}

In this chapter, the underlying biological mechanism of the obesity associated signatures from Creighton's data were investigated.
In doing so, Gatza's pathway genetic signatures were utilised to determine which biological pathways the obesity associated genetic signatures were most similar to.
First, the direction of Gatza's pathway associated genetic signatures were resolved; then the pathway associated metagenes were compared with the obesity associated metagenes; and lastly linear models were constructed based on the pathway metagenes and sample \gls{bmi}/\gls{bmi} status to predict the obesity associated metagenes.

\section{Pathway associated genetic signatures from \citet{Gatza2010a} study}
\label{sec:pathway_associated_genetic_signatures_from_gatza2010a_study}

First, the direction of Gatza's pathway associated genetic signatures were resolved

\section{Pathway associated metagenes and obesity associated metagenes}
\label{sec:pathway_associated_metagenes_and_obesity_associated_metagenes}

then the pathway associated metagenes were compared with the obesity associated metagenes

\section{Prediction of obesity associated metagene with pathway associate metagene}
\label{sec:prediction_of_obesity_associated_metagene_with_pathway_associate_metagene}

and lastly linear models were constructed based on the pathway metagenes and sample \gls{bmi}/\gls{bmi} status to predict the obesity associated metagenes.
